### 2009-02-23 doc/storage_system/arc-storage-manual.tex
arc storage manual skeleton

%%%%---- The title ----
{\centering \textsc{\Large User's manual of the ARC storage system}\Large \par}
\vspace*{0.5cm}

@@

\tableofcontents                          %Comment if use article style
\newpage

@@

\chapter{Quick start guide} % (fold)
\label{cha:quick_start_guide}

\section{Checking the code out from the subversion} % (fold)
\label{sec:checking_the_code_out_from_the_subversion}

% section checking_the_code_out_from_the_subversion (end)

\section{Compiling and installing} % (fold)
\label{sec:compiling_and_installing}

% section compiling_and_installing (end)

\section{Modifying the configuration template} % (fold)
\label{sec:modifying_the_configuration_template}

% section modifying_the_configuration_template (end)

\section{Running the daemon} % (fold)
\label{sec:running_the_daemon}

% section running_the_daemon (end)

\section{Using the CLI tool} % (fold)
\label{sec:using_the_cli_tool}

% section using_the_cli_tool (end)

% chapter quick_start_guide (end)

\chapter{Installing the system} % (fold)
\label{cha:installing_the_system}

\section{Getting the source code} % (fold)
\label{sec:getting_the_source_code}

% section getting_the_source_code (end)

@@

\subsection{HED service config} % (fold)
\label{sub:hed_service_config}

% subsection hed_service_config (end)

\subsection{Centralized A-Hash} % (fold)
\label{sub:centralized_a_hash}

% subsection centralized_a_hash (end)

\subsection{Distributed A-Hash} % (fold)
\label{sub:distributed_a_hash}

% subsection distributed_a_hash (end)

\subsection{Librarian} % (fold)
\label{sub:librarian}

% subsection librarian (end)

\subsection{Shepherd} % (fold)
\label{sub:shepherd}

% subsection shepherd (end)

\subsection{Hopi} % (fold)
\label{sub:hopi}

% subsection hopi (end)

\subsection{Bartender} % (fold)
\label{sub:bartender}

% subsection bartender (end)

\subsection{Configuring inter-service trust} % (fold)
\label{sub:configuring_inter_service_trust}

% subsection configuring_inter_service_trust (end)

\subsection{Virtual organizations} % (fold)
\label{sub:virtual_organizations}

% subsection virtual_organizations (end)

@@

\section{Single node} % (fold)
\label{sec:single_node}

% section single_node (end)

\section{Centralized management} % (fold)
\label{sec:centralized_management}

% section centralized_management (end)

\section{Simple distribution} % (fold)
\label{sec:simple_distribution}

% section simple_distribution (end)

\section{One service per node} % (fold)
\label{sec:one_service_per_node}

% section one_service_per_node (end)

% chapter installing_the_system (end)

\chapter{Using the system} % (fold)
\label{cha:using_the_system}

@@

\subsection{Configuring the command line tool} % (fold)
\label{sub:configuring_the_command_line_tool}

% subsection configuring_the_command_line_tool (end)

\subsection{Creating the root collection} % (fold)
\label{sub:creating_the_root_collection}

% subsection creating_the_root_collection (end)

\subsection{Uploading files} % (fold)
\label{sub:uploading_files}

% subsection uploading_files (end)

\subsection{Creating collections} % (fold)
\label{sub:creating_collections}

% subsection creating_collections (end)

\subsection{Moving files} % (fold)
\label{sub:moving_files}

% subsection moving_files (end)

\subsection{Creating hardlinks} % (fold)
\label{sub:creating_hardlinks}

% subsection creating_hardlinks (end)

\subsection{Removing files} % (fold)
\label{sub:removing_files}

% subsection removing_files (end)

\subsection{Removing collections} % (fold)
\label{sub:removing_collections}

% subsection removing_collections (end)

\subsection{Close collections} % (fold)
\label{sub:close_collections}

% subsection close_collections (end)

\subsection{Modify access policies} % (fold)
\label{sub:modify_access_policies}

% subsection modify_access_policies (end)

\subsection{Working with mount points} % (fold)
\label{sub:working_with_mount_points}

% subsection working_with_mount_points (end)

@@

@@

\subsection{Configuring the FUSE module} % (fold)
\label{sub:configuring_the_fuse_module}

% subsection configuring_the_fuse_module (end)

\subsection{Mounting the storage system} % (fold)
\label{sub:mounting_the_storage_system}

% subsection mounting_the_storage_system (end)

\subsection{Supported operations} % (fold)
\label{sub:supported_operations}

% subsection supported_operations (end)

\subsection{Limitations} % (fold)
\label{sub:limitations}

% subsection limitations (end)

@@

% chapter using_the_system (end)

>>>>

%%%%---- The title ----
{\centering \textsc{\Large Administrator's and user's manual of the ARC storage system}\Large \par}
\vspace*{0.5cm}

@@

\tableofcontents                          %Comment if use article style
\begin{verbatim}
    Administrator's and user's manual
    ---------------------------------

    Administrator's manual
    - Quick start guide
        - Checking the code out from the subversion
        - Compiling and installing
        - Modifying the configuration template
        - Running the daemon
        - Using the CLI tool
    - Installation:
        - Getting the source code from subversion
        - Compilation details
        - Installation
    - Configuration:
        - HED service config
        - Centralized A-Hash
        - Distributed A-Hash
        - Librarian
        - Shepherd
        - Hopi
        - Bartender
        - Configuring inter-service trust: local listing of DNs, or using an A-Hash to store them
        - Virtual organizations: how to configure HED to trust a VO
    - Deployment scenarios:
        - Single node: putting every service on one single node (including a storage node with Hopi)
        - Centralized management: using seperate multiple storage nodes with Hopi, but leaving a central A-Hash, a Librarian and a Bartender on the central node
        - Simple distribution: split the central node to three nodes, each of them has an A-Hash, a Librarian and a Bartender, and we have separate storage nodes
        - One service per node: we have seperate nodes for all the services, any number of A-Hash nodes, any number of Librarian nodes, Bartender nodes, storage nodes

    User's manual
    - Overview: what do you need to access a running ARC storage system
    - Prototype command line tool
        - Configuring the command line tool
        - Creating the root collection
        - Uploading files
        - Creating collections
        - Moving files
        - Creating hardlinks
        - Removing files
        - Removing collections
        - Close collections
        - Modify access policies
        - Working with mount points
    - Grid jobs
        - Configuring the ARC storage DMC
        - Specifying files in job descriptions
    - Accessing the system with FUSE
        - Configuring the FUSE module
        - Mounting the storage system
        - Supported operations
        - Limitations

\end{verbatim}

\newpage

@@

\chapter{Administrator's manual} % (fold)
\label{cha:administrator_s_manual}

\section{Quick start guide} % (fold)
\label{sec:quick_start_guide}

\begin{verbatim}
http://svn.nordugrid.org/
svn co http://svn.nordugrid.org/repos/nordugrid/arc1/trunk arc1   
README file for dependencies
$ ./autogen.sh
$ ./configure --disable-java --disable-a-rex-service --disable-isi-service --disable-charon-service --disable-compiler-service --disable-paul-service --disable-sched-service
--prefix

Unit testing:       yes
Java binding:       no
Python binding:     yes (2.5)

Available third-party features:

RLS:                yes
GridFTP:            yes
LFC:                no
RSL:                yes
SAML:               yes
MYSQL CLIENT LIB:   no
gSOAP:              no

Included components:
A-Rex service:      no
ISI service:        no
CHARON service:     no
HOPI service:       yes
SCHED service:      no
STORAGE service:    yes
PAUL service:       no
SRM client (DMC):   no
GSI channel (MCC):  yes

$ make

$ sudo make install

\end{verbatim}

% section quick_start_guide (end)

\section{Installation} % (fold)
\label{sec:installation}

% section installation (end)

@@

@@

% chapter administrator_s_manual (end)

\chapter{User's manual} % (fold)
\label{cha:user_s_manual}

\section{Overview} % (fold)
\label{sec:overview}

% section overview (end)

@@

@@

\section{Grid jobs} % (fold)
\label{sec:grid_jobs}

% section grid_jobs (end)

@@

@@

% chapter user_s_manual (end)
